Homicide Increases in the COVID-19 Era

### 2025-02-25 Draft1.qmd
fixed appendix

# Plots

@@

@@

Now, using this joined dataset, create six maps, one for each year.

@@

## Basic Regression Between Median Income and Crimes per Zip Code

@@

@@

@@

# Appendix {.unnumbered}

@@

## Figure 1 - Examining Crime Density from 2010–2019 and 2020-Present {.unnumbered}

@@

## Figure 2 - Examining Number Of Crimes Over Time {.unnumbered}

@@

## Figure 3 - Crime rate frequency by day of the week {.unnumbered}

@@

## Figure 5 - Median Household Income by Zip Code in Los Angeles by Year {.unnumbered}

@@

## Figure 6 - Crime Rates Compared to Median Household Income {.unnumbered}

>>>>

# Exploratory Data Analysis

@@

abline(h = pretty(weekly_counts$Crimes), v = pretty(weekly_counts$Index), 
       col = "gray", lty = "dotted")
```
### Interpretation

@@

@@

## Regression Between Median Income and Crimes per Zip Code

@@

# summary(lm_income_crimes)

@@

## ggplot2 ideas

* histogram (we did a barplot)
* boxplots!
* geom_tile - correlations
*

@@

# Appendices {.appendix}

@@

# Figure 1 - Examining Crime Density from 2010–2019 and 2020-Present {.unnumbered}

@@

# Figure 2 - Examining Number Of Crimes Over Time {.unnumbered}

@@

# Figure 3 - Crime rate frequency by day of the week {.unnumbered}

@@

# Figure 5 - Median Household Income by Zip Code in Los Angeles by Year {.unnumbered}

@@

# Figure 6 - Crime Rates Compared to Median Household Income {.unnumbered}
